Decentralised Authoring, Annotations and Notifications for a Read-Write Web with dokieli

### 2017-04-07 index.tex
syntax

\par The tools that provide good collaborative editing UIs appear to do so at the expense of data ownership and interoperability; those which promote creation and publication of data in open reusable formats are lacking facilities for linking discourse and conversation to concepts published. Decentralised creations also mean that each author can choose their own semantics (e.g. their own vocabulary to annotate RDF), and then such decentralised documents can link to each other and their schemas can also be mapped to each other, whereas in centralised platforms this is (if they support semantics at all) often prescribed, either technically enforced, or encouraged by social convention.

@@

\par Decentralised read-write environments make it possible for different actors (e.g., authors, reviewers) to have their own personal online storages where they can: manage their data; have socially-aware access controls on the data (e.g., who gets to see and update what); send notifications based on their interactions; and permit different applications to operate on the data, including moving the data from one server to another seamlessly. Figure ~\ref{fig:centralised-decentralised-architectures} depicts the contrast between typical centralised and decentralised architectures.

>>>>

\par The tools that provide good collaborative editing UIs appear to do so at the expense of data ownership and interoperability; those which promote data creation and publication in open reusable formats are lacking facilities for linking discourse and conversation to concepts published. Decentralised creations also mean that each author can choose their own semantics (e.g. their own vocabulary to annotate RDF), and then such decentralised documents can link to each other and their schemas can also be mapped to each other, whereas in centralised platforms this is (if they support semantics at all) often prescribed, either technically enforced, or encouraged by social convention.

@@

\par Decentralised read-write environments make it possible for different actors (e.g., authors, reviewers) to have their own personal online storages where they can: manage their data; have socially-aware access controls on the data (e.g., who gets to see and update what); send notifications based on their interactions; and permit different applications to operate on the data, including moving the data from one server to another seamlessly. Figure~\ref{fig:centralised-decentralised-architectures} depicts the contrast between typical centralised and decentralised architectures.
